This page and the next page should be removed

### 2022-01-31 analysis/manuscript.Rmd
Update preprocessing

# Directory paths
data_dir <- here("data")
output_dir <- here("output")

# File paths
trials_file <- here(output_dir, "all_trials.csv")
models_file <- here(output_dir, "models.RDS")
```

@@

# Process EEG data
res <- pipeline$group_pipeline(
  vhdr_files = vhdr_files,
  log_files = logs,
  export_dir = output_dir,
  downsample_sfreq = 256.,
  # bad_channels = "auto",
  ocular_correction = "fastica",
  highpass_freq = 0.1,
  lowpass_freq = 30.,
  triggers = c(221, 222),
  epochs_tmin = -0.5,
  epochs_tmax = 1.5,
  baseline = c(-0.2, 0.0),
  reject_peak_to_peak = 200.,
  reject_flat = 1.,
  components = list(
    "name" = c("P1", "N170", "N400"),
    "tmin" = c(0.1, 0.15, 0.4),
    "tmax" = c(0.15, 0.2, 0.7),
    "roi" = list(
      c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
      c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
      c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
    )
  ),
  average_by = c("phase/condition"),
  perform_tfr = FALSE,
  perm_contrasts = list(
    c("Pre-insight/Informed", "Pre-insight/Naive"),
    c("Insight/Informed", "Insight/Naive"),
    c("Post-insight/Informed", "Post-insight/Naive")
  ),
  n_jobs = 1
)

# Extract results
trials <- tibble(res[[1]])
evokeds <- tibble(res[[2]])
clusters <- tibble(res[[3]])
# tfr_evokeds <- tibble(res[[4]])
# tfr_clusters <- tibble(res[[5]])
```

```{r, modeling, eval=run$modeling}
# Read single trial data
read_csv(trials_file, col_types = cols(
  participant_id = col_factor(),
  item_id = col_factor(),
  phase = col_factor(),
  condition = col_factor()
)) %>%
  # Mark unrealistically short RTs
  mutate(rt = ifelse(rt < 200, NA, rt))

@@

>>>>

# Directory paths
data_dir <- here("data")
output_dir <- here("output")
report_dir <- here(output_dir, "html_reports")

# File paths
trials_file <- here(output_dir, "all_trials.csv")
clusters_file <- here(output_dir, "clusters.csv")
models_file <- here(output_dir, "models.RDS")
```

@@

# Process EEG data
res <- pipeline$group_pipeline(
  vhdr_files = vhdr_files,
  log_files = logs,
  export_dir = output_dir,
  report_dir = report_dir,
  downsample_sfreq = 250.,
  bad_channels = NULL,
  ocular_correction = "fastica",
  highpass_freq = 0.1,
  lowpass_freq = 40.,
  triggers = c(221, 222),
  epochs_tmin = -0.5,
  epochs_tmax = 1.5,
  baseline = c(-0.2, 0.0),
  reject_peak_to_peak = 200.,
  reject_flat = 1.,
  components = list(
    "name" = c("P1", "N170", "N400"),
    "tmin" = c(0.1, 0.15, 0.4),
    "tmax" = c(0.15, 0.2, 0.7),
    "roi" = list(
      c("PO3", "PO4", "POz", "O1", "O2", "Oz"),
      c("P7", "P8", "PO7", "PO8", "PO9", "PO10"),
      c("C1", "C2", "Cz", "CP1", "CP2", "CPz")
    )
  ),
  average_by = c("phase/condition"),
  perform_tfr = TRUE,
  perm_contrasts = list(
    c("Pre-insight/Informed", "Pre-insight/Naive"),
    c("Insight/Informed", "Insight/Naive"),
    c("Post-insight/Informed", "Post-insight/Naive")
  ),
  n_jobs = 1
)
```

```{r, modeling, eval=run$modeling}
# Read single trial data
read_csv(trials_file, col_types = cols(
  participant_id = col_factor(),
  item_id = col_factor(),
  phase = col_factor(),
  condition = col_factor()
)) %>%
  # Mark unrealistically short RTs
  mutate(rt = ifelse(rt < 200, NA, rt)) -> trials

@@

```{r, clusters, include=TRUE}
read_csv(clusters_file, col_types = cols(
  contrast = col_factor(levels = c(
    "Pre-insight/Informed - Pre-insight/Naive",
    "Insight/Informed - Insight/Naive",
    "Post-insight/Informed - Post-insight/Naive"
  ))
)) %>%
  pivot_longer(-c(contrast, stat, time), names_to = "channel") %>%
  pivot_wider(names_from = stat, values_from = value) %>%
  ggplot(aes(x = time, y = channel, fill = p_val)) +
  facet_grid(~contrast) +
  geom_raster() +
  scale_fill_viridis_c()
ggsave("clusters.pdf")
```
